%
%Academic CV LaTeX Template
% Author: Dubasi Pavan Kumar
% LinkedIn: https://www.linkedin.com/in/im-pavankumar/
% License: MIT
%
% For errors, suggestions, or improvements, please contact:
% Email: pavankumard.pg19.ma@nitp.ac.in
%

\documentclass[a4paper,11pt]{article}

% Package imports
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\usepackage{fontawesome5}

% Color definitions
\definecolor{darkblue}{RGB}{0,0,139}

% Page layout
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
\setlength{\footskip}{5pt} % Addressing fancyhdr warning

% Hyperlink setup (moved after fancyhdr to address warning)
\usepackage[hidelinks]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,
    urlcolor=darkblue,
}

% Custom box settings
\usepackage[most]{tcolorbox}
\tcbset{
    frame code={},
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!20,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=-2mm,
    boxsep=4pt,
    arc=0pt,outer arc=0pt,
}

% URL style
\urlstyle{same}

% Text alignment
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\circ$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm,itemsep=0.5mm]}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%

% Commands for icon sizing and positioning
\newcommand{\socialicon}[1]{\raisebox{-0.05em}{\resizebox{!}{1em}{#1}}}
\newcommand{\smallicon}[1]{\raisebox{-0.3em}{\resizebox{!}{1.3em}{#1}}}

% Font options
\newcommand{\headerfonti}{\fontfamily{phv}\selectfont} % Helvetica-like (similar to Arial/Calibri)
\newcommand{\headerfontii}{\fontfamily{ptm}\selectfont} % Times-like (similar to Times New Roman)
\newcommand{\headerfontiii}{\fontfamily{ppl}\selectfont} % Palatino (elegant serif)
\newcommand{\headerfontiv}{\fontfamily{pbk}\selectfont} % Bookman (readable serif)
\newcommand{\headerfontv}{\fontfamily{pag}\selectfont} % Avant Garde-like (similar to Trebuchet MS)
\newcommand{\headerfontvi}{\fontfamily{cmss}\selectfont} % Computer Modern Sans Serif
\newcommand{\headerfontvii}{\fontfamily{qhv}\selectfont} % Quasi-Helvetica (another Arial/Calibri alternative)
\newcommand{\headerfontviii}{\fontfamily{qpl}\selectfont} % Quasi-Palatino (another elegant serif option)
\newcommand{\headerfontix}{\fontfamily{qtm}\selectfont} % Quasi-Times (another Times New Roman alternative)
\newcommand{\headerfontx}{\fontfamily{bch}\selectfont} % Charter (clean serif font)

\begin{document}
\headerfontiii

% Header
\begin{center}
    {\Huge\textbf{Zirui Zhang}}
\end{center}
\vspace{-6mm}

\begin{center}
    \small{
    \socialicon{\faLinkedin} \href{https://www.linkedin.com/in/zirui-zhang-924958319/}{Zirui Zhang} | 
    \socialicon{\faGithub} \href{https://github.com/zhangzrjerry}{ZhangzrJerry} | 
    \socialicon{\faOrcid} \href{https://orcid.org/0009-0008-4156-1652}{0009-0008-4156-1652}
    }
\end{center}
\vspace{-6mm}
\begin{center}
    \small{Hong Kong / Guangzhou / Shenzhen - China}
\end{center}

\vspace{-4mm}

\section{\textbf{Education}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeSubheading
{Hong Kong University of Science and Technology}{Hong Kong, China}
{Bachelor of Engineering}{Sep. 2024 - Present}
\resumeItemListStart
\item GPA: 3.69/4.30
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-6mm}

\section{\textbf{Experience}}
\vspace{-0.4mm}
  \resumeSubHeadingListStart
  \resumeSubheading
      {{Next Innovation STEM Center [\href{https://nifornextinnovation.com}{\textcolor{darkblue}{\faIcon{globe}}}]}}{Guangzhou, China}
      {Robotics Engineer}{Sep. 2024 - Present}
      \resumeItemListStart
        \item Responsible for the development of planning and control in locomotion robot
      \resumeItemListEnd 
  \resumeSubheading
    {{Rhino-Bird Middle School Science Research Training Program [\href{https://ur.tencent.com/}{\textcolor{darkblue}{\faIcon{globe}}}]}}{Remote}
    {Research Intern}{Jun. 2023 - Oct. 2023}
    \resumeItemListStart
      \item Supervised by Professor Chuan Shi from BUPT
      \item Developed an intelligent book recommendation system to improve the accuracy of public library services
      \item Won the Excellent Award in 2023 Rhino-Bird Middle School Science Research Training Program
    \resumeItemListEnd
  \resumeSubheading
    {{Guangzhou Yingcai Middle School Science Research Training Program [\href{https://jyj.gz.gov.cn/gkmlpt/content/7/7875/post_7875383.html}{\textcolor{darkblue}{\faIcon{globe}}}]}}{Guangzhou, China}
    {Research Trainee}{Jan. 2022 - Aug. 2022}
    \resumeItemListStart
      \item Supervised by Professor Yi Cai from SCUT
      \item Focused on the construction of knowledge graph
    \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-6mm}

\section{\textbf{Involvement}}
\vspace{-0.4mm}
\resumeSubHeadingListStart
\resumeProject
  {FIRST Robotics Competition Team 8214 [\href{https://www.thebluealliance.com/team/8214}{\textcolor{darkblue}{\faIcon{globe}}}]}
  {Program Mentor}
  {Sep. 2024 - Present}
  {Guangzhou, China}
\resumeItemListStart
  \item Responsible for the development of the FRC robotics control system
\resumeItemListEnd

\resumeProject
  {FIRST Robotics Competition Team 6399 [\href{https://www.thebluealliance.com/team/6399}{\textcolor{darkblue}{\faIcon{globe}}}]}
  {Program Mentor}
  {Jul. 2024 - Aug. 2024}
  {Jinan, China}
\resumeItemListStart
  \item Responsible for the development of the FRC robotics control system and provided programming instruction to the team
\resumeItemListEnd

\resumeProject
  {FIRST Robotics Competition Team 8811 [\href{https://www.thebluealliance.com/team/8811}{\textcolor{darkblue}{\faIcon{globe}}}]}
  {Founder, Youth Mentor}
  {Sep. 2021 - Aug. 2023}
  {Guangzhou, China}
\resumeItemListStart
  \item Established the team in my senior high school and raised over \$14,000 in the first year
  \item Conducted over 60 weekly studies and 3 holiday training programs for our team in 2 years
\resumeItemListEnd

\resumeProject
  {FIRST Robotics Competition Team 8011 [\href{https://www.thebluealliance.com/team/8011}{\textcolor{darkblue}{\faIcon{globe}}}]}
  {Team Captain, Program Leader}
  {Sep. 2019 - Jun. 2023}
  {Guangzhou, China}
\resumeItemListStart
  \item Led the team to the Champion in the 2020 We RoboStar Robotics League as the Program Leader
  \item Steered the team to Rookie Game Changer Award in the 2021 INFINITE RECHARGE At Home Challenge
  \item Won the Excellence in Engineering Award with my teamates in 2022 Hangzhou Regional
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-6mm}

\section{\textbf{Projects}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeProject
  {FRC 2024 Robot - Defiant}
  {Tools: JAVA, AprilTag}
  {Jun. 2024 - Aug. 2024}
  {{}[\href{https://www.bilibili.com/video/BV1pbWCejEUi}{\textcolor{darkblue}{\faVideo}}]}
\resumeItemListStart
  \item Mainly responsible for the development of AprilTag based VO and IMU Coupled Localization
\resumeItemListEnd

\resumeProject
  {Intelligent Book Recommendation and User Interest Analysis System}
  {Tools: Flask, PaddlePaddle}
  {Jun. 2023 - Oct. 2023}
  {{}[\href{https://github.com/zhangzrjerry/rhinobird}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
  \item Mainly responsible for model training and back-end database development
\resumeItemListEnd

\resumeProject
  {FRC Data Collection Software}
  {Tools: WXML, Node.js}
  {Feb. 2022 - Aug. 2022}
  {{}[\href{https://github.com/frc8811/frc_scouting}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
  \item Mainly responsible for front-end logic and back-end database development
\resumeItemListEnd

\resumeProject
  {A Single-Wheeled Self-Balancing Omni-directional Mobile Platform}
  {Tools: SolidWorks, LCEDA, C++}
  {Sep. 2021 - Mar. 2022}
  {{}[\href{https://patents.google.com/patent/CN115107901A/en}{\textcolor{darkblue}{\faFile}}]}
\resumeItemListStart
  \item Mainly responsible for control algorithms and embedded development
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-6mm}

\section{\textbf{Patents and Publications} \hfill \textcolor{darkblue}{\scriptsize C=Conference, J=Journal, T=Thesis, P=Patent, S=Software}}
\vspace{0.2mm}
\small{
\begin{enumerate}[leftmargin=*, labelsep=0.5em, align=left, widest={[\textbf{S.1}]}, itemindent=0em, label={\textbf{[\arabic*]}]}]

\item[\textbf{[S.1]}] Zirui Zhang and Yue Peng. (2023). \href{.}{\textbf{FRC Data Collection Software}}. China National Intellectual Property Administration, Patent No. 2023SR1385127. Publication Date: 2023-11-06.

\item[\textbf{[T.1]}] Zirui Zhang and Yue Peng. (2023). \href{.}{\textbf{Intelligent Book Recommendation and User Interest Analysis System Based on Factorization Machines}}. \textit{2023 Tencent Rhino-Bird Middle School Science Research Training Proogram}

\item[\textbf{[P.1]}] Liangyu Cai, Zihan Chen, Zirui Zhang et al. (2022). \href{https://patents.google.com/patent/CN115107901A/en}{\textbf{Single-wheel balance motion device}}. China National Intellectual Property Administration, Patent No. CN115107901A. Publication Date: 2022-09-27.

\end{enumerate}

\end{document}